Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-04-16 SIR_manuscript.tex
good nigh5

In order to understand the effect of testing processes on an epidemic dynamics, we deveopled a mechanistic SIR-type model with epidemic and testing components. Here, we focus on the the effect of testing intensity, different levels of testing ``focus'' (from random to highly targeted), and rate of test return on the epidemic dynamics. 
Our model provides insights to the sensitivity of the epidemiological dynamics, through $\Rnum$, with respect to the undelying epidemic and testing parameters.
\david{This paragraph does not flow from the rest of the intro, and is a weird way to end when the point of the paper is about testing.}\ali{some edits/rewording are done, ok?}

\david{There is some back and forth between generic discussion and \covid-specific comments.  I think COVID should be used as motivation, but that the whole paper should be framed generically.}

>>>>

In order to understand the effect of testing processes on an epidemic dynamics, we deveopled a mechanistic SIR-type model with epidemic and testing components. Here, we focus on the the effect of testing intensity, different levels of testing ``focus'' (from random to highly targeted), and rate of test return on the epidemic dynamics. 
Our model provides insights to the sensitivity of the epidemiological dynamics, through $\Rnum$, with respect to the undelying epidemic and testing parameters.
\ali{edited in response to David comments.}
